---
title: "fluxweb Workflow"
author: "Jim Junker"
date: "January 10, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fluxweb)
library(knitr)
#colnames
```

Here is a step-by-step introduction to working with the fluxweb package, assciated data, and another novel example. First steps are to install and load the package:

`install.packages("fluxweb")`

Load the package

`library(fluxweb)`

The *fluxweb* package comes with three data sets that represent three levels of complexity--from a species-specific level with 62 individual nodes to a simple case with four aggregated groupings (Figure 1).

![configurations of data sets found in the fluxweb package](`r paste(getwd(),"/README-files/Gauzens-et-al-2017_fig-1.png",sep = "")`)

These data sets can be viewed by calling `data()`:

`data(package="fluxweb")`

They all have the generally the same structure, a list of five items:

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; $mat: a binary feeding matrix of *i* resources (rows) and *j* consumers (columns)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; $biomasses:  vector of standing biomass for each node  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; $bodymasses:  vector of body sizes for each node  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Alternatively, this could be $met.rate:  vector of metabolic rates for each node  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; $efficiencies:  vector of feeding efficiencies. What this values represents (e.g., assimilation efficiency, gross production efficiency, etc.) depends on the loss term used in *bodymasses*  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; $names: vector of names for the rows/columns  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Alternatively, this can be a data.frame with species names, some trophic grouping, trophic level, etc. (see `groups.level` in  example).

<center>
Figure 2. Feeding interaction matrix of the simplified case (Fig. 1c). Food resources are represented as rows and consumers are columns. 

```{r mat-table, echo = FALSE, fig.align= "center"}
colnames(simple.case$mat) <- rownames(simple.case$mat) <- simple.case$names
knitr::kable(t(simple.case$mat))
```

</center>

We will first walk through the simple case. Loading in the example as a list of length five(5):

```{r simple case, echo = T}
simple = simple.case
```

We have already explored the contents of the list above as well as the structure of the feeding matrix (Fig. 2), but for a reminder the five items are: 'mat' - feeding matrix (4 x 4), 'met.rate' - metabolic rates of each node (numeric vector, length = 4), 'biomasses' - the biomass of each node (numeric vector, length = 4), 'efficiencies' - efficiency of feeding links (numeric vector, length = 4), and 'names' - the names for each node (character vector, length = 4).

But let's look at the other items:

```{r met.rates, echo = T}
names(simple$met.rate) <- simple$names
simple$met.rate
```

```{r biomasses, echo = T}
names(simple$biomasses) <- simple$names
simple$biomasses
```

```{r efficiencies, echo = T}
names(simple$efficiencies) <- simple$names
simple$efficiencies
```

We have everything we need now to run the basic flux estimation:

```{r simple fluxing, echo = T}
mat.fluxes <- fluxing(mat = simple$mat, biomasses  = simple$biomasses, losses = simple$met.rate, efficiencies = simple$efficiencies, bioms.prefs = FALSE, bioms.losses = FALSE, ef.level = "prey")
```

`mat.fluxes` is a 4 x 4 matrix that is the material flux from resources (rows) to consumers (columns).

Figure 3. Material flux matrix from resources (rows) to consumers (columns).

```{r mat.flux table, echo = T, fig.align="center"}

colnames(simple.case['mat']$mat) <- rownames(simple.case['mat']$mat) <- simple.case['names']$names
knitr::kable(t(mat.fluxes))

```

In the species-level (a) and simple cases (c) the feeding is based on relative abundance of prey types. This is done by setting a feeding connection to '1', meaning a feeding interaction exists, but there is not preference for the prey item. Therefore, feeding rates are just based on relative abundance in the model.

stepping through the example of moderate complexity that has some aggregation of prey and food items is the most useful to understand how we can alter the interactions to 
