---
title: "fluxweb Workflow"
author: "Jim Junker"
date: "January 10, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fluxweb)
library(knitr)
```

Here is a step-by-step introduction to working with the fluxweb package, assciated data, and another novel example. First steps are to install and load the package:

`install.packages("fluxweb")`

Load the package

`library(fluxweb)`

The *fluxweb* package comes with three data sets that represent three levels of complexity--from a species-specific level with 62 individual nodes to a simple case with four aggregated groupings (Figure 1).

![configurations of data sets found in the fluxweb package](`r paste(getwd(),"/README-files/Gauzens-et-al-2017_fig-1.png",sep = "")`)

These data sets can be viewed by calling `data()` function:

`data(package="fluxweb")`

They all have the same structure, a list of five items:

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; $mat: a binary feeding matrix of *i* resources (rows) and *j* consumers (columns)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; $biomasses:  vector of standing biomass for each node  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; $bodymasses:  vector of body sizes for each node  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Alternatively, this could be $met.rate:  vector of metabolic rates for each node  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; $efficiencies:  vector of feeding efficiencies. What this values represents (e.g., assimilation efficiency, gross production efficiency, etc.) depends on the loss term used in *bodymasses*

```{r mat-table, echo = FALSE}
knitr::kable(simple.case[['mat']])
```

The species-level and simple cases are binary, connectance webs. They only show if a feeding interaction exists, there are no consumer diets preferences. Therefore, we first walk through the example of moderate complexity that has some aggregation of fo
